### 2013-05-17 CM-Scripts/studentuserlist.tex
Javapath for Mr. Heinz renamed to be valid in java package.
added writing directory of  mr zacher.

@@

\begin{table}
  \caption{CVS-Zug\"ange f\"ur Studenten, Stand: \today}
  \begin{tabularx}{\textwidth}{|l|l|l|l|l|X|l|l|}

@@

\rowcolor{yellow}\cellcolor{red}diplomand5   & zacher    &Dirk Zacher     &dirk.zacher@fernuni-hagen.de&                      &18.4.13     &\cellcolor{red}Laptop\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand6   & floheinz &Florian Heinz    &fh@sysv.de         &Algebras/RegionInterpolation2 und Javagui/viewer/3d &26.4.13 &\\

@@

  \end{tabularx}
\end{table}

>>>>

\usepackage{longtable}

@@

\section{CVS-Zug\"ange f\"ur Studenten, Stand: \today}
\begin{longtable}{|l|l|l|l|l|l|l|l|}

@@

\rowcolor{yellow}\cellcolor{red}diplomand5   & zacher    &Dirk Zacher     &dirk.zacher@fernuni-hagen.de&Algebras/Tile      &18.4.13     &\cellcolor{red}Laptop\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand6   & floheinz &Florian Heinz    &fh@sysv.de         &Algebras/RegionInterpolation2 und Javagui/viewer/v3d &26.4.13 &\\

@@

\end{longtable}
